Enhancing the prediction of sales for newly published books by means of computational intelligence methods

### 2016-05-04 paper.tex
Reviewing Introduction pt. I

Publishing a book, in the same way as releasing any other cultural product with a physical substrate, implies several types of risks and costs due to
the complexity, and derived expenses, of the production,
distribution and storage processes; most of these costs are associated
to the number of books actually printed. But the problem is further
complicated for completely new products, in the sense that there is an unknown
author or a new topic with no track record. Sales forecasts can
only be based on the knowledge obtained from other similar products,
but the definition of ``similar'' itself is fuzzy and, sometimes,
subjective. Even if the author or the topic is known, doing accurate
estimations of future sales of the new product is quite difficult, and extremely important, so that production runs heed predicted sales. 
Indeed,several studies have demonstrated that improving sales predictions 
(a reduction of forecasting errors) results in an enhancement in the 
production process \cite{Fildes2010,Saeed2008}.

@@

In this sense, errors in one or the other direction do not have the same impact, however, it is extremely important to develop an accurate predictive method
which could forecast the future sales a new book will achieve, in order to optimise production schedules, improve the publishing company profits and minimise losses \cite{Zhao2001}, being this the main objective of this paper.

>>>>

Publishing a book, in the same way as releasing any other cultural product with a physical substrate, implies several types of risks and costs due to
the complexity, and derived expenses, of the production,
distribution, and storage processes; most of these costs are associated
to the number of books actually printed. But the problem is further
complicated for completely new products, in the sense that there is an unknown
author or a new topic with no track record. Sales forecasts can
only be based on the knowledge obtained from other similar products,
but the definition of ``similar'' itself is fuzzy and, sometimes,
subjective. Even if the author or the topic is known, doing accurate
estimations of future sales of the new product is quite difficult, and extremely important, so that production runs heed predicted sales. 
Indeed,several studies have demonstrated that improving sales predictions 
(a reduction of forecasting errors) results in an enhancement in the 
production process \cite{Fildes2010,Saeed2008}.

@@

Despite the fact that errors in one or the other direction do not have the same impact, it is extremely important to develop an accurate predictive method
which could forecast the future sales a new book will achieve, in order to optimise production schedules, improve the publishing company profits and minimise losses \cite{Zhao2001}, being the latter the main objective of this paper.
